---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"roller"` is a minimal [R](http://www.r-project.org/) package 
that provides functions to simulate the rolling of an `n` sided objet `t` times.
This package is perfect for simple statistical modeling of any named `n` sided object. 

* `device()` creates a coin object (of class `"device"`)
* `roll()` tosses a coin object, producing a `"roll"` object.
* `plot()` method for a `"roll"` object to plot frequencies of heads.
* `summary()` method for a `"roll"` object (of class `"summary.rolls"`)

## Motivation

This package was developed further build my personal package building skills.
Thanks to [Gaston Sanchez](http://www.gastonsanchez.com/) for the code inspiration, 
which can be found [here](https://github.com/gastonstat/cointoss). This package is an
addition/similar implimentation to the package he made.

## Usage Example

```{r examples}

library(roller)
# default
basic_device <- device()
basic_device

# one roll
roll1 <- roll(device = basic_device)
roll1

# multiple Roll
roll100 <- roll(device = basic_device, times = 100)

# summarizing the roll
summary(roll100)

# plot the multiple rolls
plot(roll100)
```

